Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 ms.tex

To investigate the possibility that such wide companions exist, we
query the ninth data release of the Sloan Digital Sky Survey
\citep[SDSS DR9,][]{Ahn12} for all stars within 25\arcsec\ with
$\Delta r < 8$ relative to each object of interest.  
Each such companion star has a ``maximum depth'' that it could cause
as a diluted ``transit'' signal, corresponding to a total eclipse 
of the hypothetical 
background binary system, inducing a 50\% flux decrement in the 
background star's apparent brightness.
Table 5 lists the 11 such stars (plus one detected in AO imaging),
whose maximum depth is at least as deep 
as the observed transit depth, thus making them possible contaminants.

@@

SDSS is 95\% complete at $r=22.2$ and the telescope has a point
spread function of $1\farcs4$. 
For the purposes of the \texttt{vespa} calculation, we thus
treat nondetection in SDSS data as providing a contrast curve at 
wide separations
down to a limiting magnitude of $r=22.2$.

>>>>

To investigate the possibility that such wide companions exist,
we query the ninth data release of the Sloan Digital Sky Survey
\citep[SDSS DR9,][]{Ahn12}.
For each target, from the depth of the observed transit we determine how
bright a background object must be to cause the event if the background
object were an equal mass totally-eclipsing binary.
We then search for all stars within 25\arcsec\ that are within this brightness
limit relative to the candidate host star.
All apertures we use in our \KT\ analysis are smaller than 20\arcsec\ so this
search should encompass the region where possible background 
contaminants could reside.
Of the 31 stars in our sample, eleven have such a companion, plus one
detected in AO imaging.

Unlike the original \kep\ field, the field for \KT\ \Ci\ is
well out of the galactic plane, so the rate of giant, distant background
stars is significantly lower.
We include all potential contaminants in Table 5.
We validate or eliminate each of these as a possibility based on the transit shape.
For example, the events near EPIC 201546283 could only be caused by a 
background binary if the background object was a completely-eclipsing system
(so that the eclipse depth was $50\%$). 
In this case, the transit would be perfectly V-shaped.
Since it is not, we can rule out the possibility this background object causes
the transit event.

In Table 5, the ``maximum depth'' column represents
the maximum observed ``transit'' depth if the transit were actually caused
by a total eclipse of the hypothetical background binary system, inducing
a 50\% flux decrement in the background star's apparent brightness.

@@

SDSS is 95\% complete at $r=22.2$ mag and the telescope has a point
spread function of $1\farcs4$. 
For the purposes of the \texttt{vespa} calculation, we thus
treat nondetection in SDSS data as providing a contrast curve at 
wide separations
down to a limiting magnitude of $r=22.2$ mag.
